---
title: "Codebook for peer-graded assignment week 4 of module 03 Getting and Cleaning the Data"
author: "me!"
date: "3/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Warning

Before running the script peer-graded.R, be aware that this script will: \
- install packages dplyr and stringr in the default directory if there are not installed yet\
- clean all your variables in the global environment at the beginning of the script\
- clean all intermediate variables at the end of the script\newline
- a temporary directory will be created in your current working directory, called DELETEME_612. The working directory will be then set to this DELETEME_612, and set back to your current directory at the end of the script.\
- If there is already a directory called DELETEME_612 in your working directory, there will be an error message. This will be the case if you are trying to rerun the script. Please remove the directory called DELETEME_612 before rerunning.  \

## About the experiment 
The experiments have been carried out with a group of **30 volunteers** within an age bracket of 19-48 years. Each person performed **six activities (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING)** wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. \

## Results \
### Elements in Global Environment\
After running the script, you will be left with 5 elements in your environment:\
- **Q1_mergedf**: the data frame that answers Q1 after merging test and train dataset\
- **Q2_selectdf**: after selecting column containing either mean or standard deviation\
- **Q3_selectdf_label**: with descriptive activity names\
- **Q4_selectdf_label**: with optimized naming\
- **Q5_mean_by_gr**: a tidy dataset containing the mean by group for each column of Q4 dataset. This table is saved into a file in the temporary eorking directory, called _peer_graded_tidyTable.txt_ (see comments in the script _peer_graded.R_ for information about location)\


### About the final table
The last table Q5_mean_by_gr is a tidy table containing 180 observations of 81 variables. 
Variables are mean or standard deviation of movement indicators. They have been averaged for each "group", a group being a unique combination of person and activity type. 
A full description of the variables is provided in the table below. A link showing distribution and missing values (if any) are stored in:\
- distribution.html
- figures



````{r , echo= FALSE}
library(knitr)
load("data.Rdata")
kable(Variables)
````
